Temporal stability in human interaction networks (Supporting Information document)

### 2016-08-17 paper.tex
arrumado do clustering e simetria

\begin{abstract}
    This paper reports on stable (or invariant) properties of human interaction networks,
with benchmarks derived from public email lists. Activity along time and topology were observed in snapshots in a timeline, 
and at different scales. Our analysis shows that activity is practically the same for all networks across timescales ranging from seconds to months. The most important metrics to the dispersion of participants in the topological measures space are related to centrality (degree, strength and betweenness), followed by symmetry-related metrics and then clustering coefficient. The activity of participants follows the expected scale-free trace, thus yielding the hub, intermediary and peripheral classes of vertices by comparison against the Erd\"os-R\'enyi model. The relative sizes of these three sectors are essentially the same for all email lists and the same along time. Typically, 3-12\% of the vertices are hubs, 15-45\% are intermediary and 44-81\% are peripheral vertices. Similar results for the distribution of participants in the three sectors and for the relative importance of the topological metrics were obtained for 12 additional networks from Facebook, Twitter and Participabr. These properties are consistent with the literature and may be general for human interaction networks, which has important implications for establishing a typology of participants based on quantitative criteria.
\end{abstract}

@@

According to Table~\ref{tab:pcain} and Figure~\ref{fig:sym},
dispersion is larger in symmetry-related metrics than in clustering coefficient.
% As expected from basic complex network theory, peripheral vertices have low values of centrality metrics and larger dispersion with regard to the clustering coefficient.
% %The scatter plot in the third system of Figure~\ref{fig:sym},
% %where all metrics are considered and there is a greater dispersion
% %with respect to the ordinates,
% This reflects in the relevance of the symmetry-related metrics.
We conclude that the symmetry metrics are more powerful, in terms of dispersion in the topological measures space, in characterizing interaction networks and their participants, than the clustering coefficient, especially for hubs and intermediary vertices (peripheral vertices have larger dispersion with regard to the clustering coefficient).
Interestingly, the clustering coefficient is always combined
with the standard deviation of the asymmetry and disequilibrium
of edges $\sigma^{asy}$ and $\sigma^{dis}$.

>>>>

\begin{abstract}
    This paper reports on stable (or invariant) properties of human interaction networks,
with benchmarks derived from public email lists. Activity along time and topology were observed in snapshots in a timeline, 
and at different scales. Our analysis shows that activity is practically the same for all networks across timescales ranging from seconds to months.
% The most important metrics to the dispersion of participants in the topological measures space are related to centrality (degree, strength and betweenness), followed by symmetry-related metrics and then clustering coefficient.
The principal components of the participants in the topological measures space remain practically unchanged as different sets of messages are considered.
The activity of participants follows the expected scale-free trace, thus yielding the hub, intermediary and peripheral classes of vertices by comparison against the Erd\"os-R\'enyi model. The relative sizes of these three sectors are essentially the same for all email lists and the same along time. Typically, 3-12\% of the vertices are hubs, 15-45\% are intermediary and 44-81\% are peripheral vertices. Similar results for the distribution of participants in the three sectors and for the relative importance of the topological metrics were obtained for 12 additional networks from Facebook, Twitter and Participabr. These properties are consistent with the literature and may be general for human interaction networks, which has important implications for establishing a typology of participants based on quantitative criteria.
\end{abstract}

@@

According to Table~\ref{tab:pcain} and Figure~\ref{fig:sym},
dispersion is larger in symmetry-related metrics than in clustering coefficient.
% As expected from basic complex network theory, peripheral vertices have low values of centrality metrics and larger dispersion with regard to the clustering coefficient.
% %The scatter plot in the third system of Figure~\ref{fig:sym},
% %where all metrics are considered and there is a greater dispersion
% %with respect to the ordinates,
% This reflects in the relevance of the symmetry-related metrics.
We conclude that the symmetry metrics are more powerful, in terms of dispersion in the topological measures space, in characterizing interaction networks and their participants, than the clustering coefficient, especially for hubs and intermediary vertices (peripheral vertices have larger dispersion with regard to the clustering coefficient).
Interestingly, the clustering coefficient is always combined
with the standard deviation of the asymmetry and disequilibrium
of edges $\sigma^{asy}$ and $\sigma^{dis}$ in the third principal component.

### 2016-08-17 supportingInformation.tex
arrumado do clustering e simetria

\subsection{Temporal circular measures}\label{si:circ}
The metrics with which we report measurements and results
of activity along time are the rescaled circular mean $\theta_\mu'$,
the standard deviation $S(z)$, the variance $Var(z)$, the circular dispersion $\delta(z)$
and the ratio between the lowest $b_l$ and the highest $b_h$ incidences $\frac{b_l}{b_h}$ at each time scale.
Also, the mean $\mu(\frac{b_l'}{b_h'})$ and 
the standard deviation $\sigma(\frac{b_l'}{b_h'})$ 
of the relation between the minimum $b_l'$ and the maximum $b_h'$ incidences
are given for 1000 uniform distribution simulations within the 
same number of bins and with the same number of samples~\footnote{Numpy version 1.8.2, ``random.randint'' function, was used for simulations, algorithms in \url{https://pypi.python.org/pypi/gmane}}.
Greater dispersion is found on the scales of seconds and minutes, followed
by days of the month.
Greater localization is found in the scale of hours of the day, followed by weekdays and months.

>>>>

\subsection{Temporal circular measures}\label{si:circ}
The metrics with which we report measurements and results
of activity along time are the rescaled circular mean $\theta_\mu'$,
the standard deviation $S(z)$, the variance $Var(z)$, the circular dispersion $\delta(z)$
and the ratio between the lowest $b_l$ and the highest $b_h$ incidences $\frac{b_l}{b_h}$ at each time scale.
Also, the mean $\mu(\frac{b_l'}{b_h'})$ and 
the standard deviation $\sigma(\frac{b_l'}{b_h'})$ 
of the relation between the minimum $b_l'$ and the maximum $b_h'$ incidences
are given for 1000 uniform distribution simulations within the 
same number of bins and with the same number of samples~\footnote{Numpy version 1.8.2, ``random.randint'' function, was used for simulations, algorithms in \url{https://github.com/ttm/percolation}}.
Greater dispersion is found on the scales of seconds and minutes, followed
by days of the month.
Greater localization is found in the scale of hours of the day, followed by weekdays and months.
